Ontology Matching Paper

### 2016-05-08 milestone3/paper/paper.tex
Matching part done. Abstract missing

\section{Related Work}
%Give here an overview over related matching methods and how they related to your own solution. Cite papers that might have inspired your approach. Sometimes it makes sense to have this section immediately after the introduction.
In order to match our ontology to others, we did research about state of the art matching and alignment tools. \cite{adaptiveInformation_2014} is a comprehensive list of the top 50 tools, separating active from inactive tools. Additionally, we looked at some of the tools revised by Euzenat et Al \cite{euzenat2007ontology}. Furthermore, we looked at the participants from the most recent OAEI.

@@

\section{Methods, Algorithms and Implementation}
% Introduce your method, i.e. the overall approach taken and the general idea, the\bibliography{paper}
 algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).

% Maybe you want to separate this part into subsections for your two systems
\subsection{Ontology Matching}
\label{Ontology_Matching}
- Decided to use one of the best candidates in the OAEI of 2014, AML (AgreementMakerLight) the best system (as measured in terms of F-measure) for lightweight ontologies. The reasons behind this choice was that AML exceeded our expectations with regard to run time results, comprehensive user interface and integrated evaluation mechanism. The procedure can be fully or semi automatic, with the user being presented to a fully customizable matching. We can choose between different metrics with respect to structure,content etc 
-examples with pictures, String Matcher, Word matcher, Property matcher, Cardinality matcher and background knowledge matcher.

\begin{figure}[h]\centering
	\includegraphics[width=.75\textwidth]{img/match_city.png}
	\caption{Visual representation of a single correct match in AML.}
	\label{fig:single_match}
\end{figure}
\begin{figure}[h] \centering
	\includegraphics[width=.75\textwidth]{img/match_combo.png}
	\caption{Visual representation of multiple correct matches in AML.}
	\label{fig:multiple_match}
\end{figure}
\begin{figure}[h] \centering
	\includegraphics[width=.75\textwidth]{img/conflict_exhibition_exposition.png}
	\caption{Visual representation of an incorrect match in AML.}
	\label{fig:incorrect_match}
\end{figure}

@@

\section{Validation and Experiments}
% In a scientific paper you want to show that your choice of method and algorithms was the right choice. So, this could be a place where you make claims or ask concrete and explicit research questions (e.g. with respect to runtime and/or precision/recall.

\subsection{Group 10: Cultural Ontology}
We match to the main entities of Events and Venues.

\begin{figure}[h]\centering
	\includegraphics[width=.75\textwidth]{img/match_g10.png}
	\caption{Matching to group 10}
	\label{fig:match_g10}
\end{figure}

\subsection{Group 13: Tourist safety Ontology}

\subsection{Group 15: Activity finding Ontology}
Six correct matchings versus six incorrect matchings

\begin{figure}[h]\centering
	\includegraphics[width=.75\textwidth]{img/match_g15.png}
	\caption{Matching to group 15}
	\label{fig:match_g15}
\end{figure}

\section{Results and Discussion}
% Give here details about the most important results of your experiments. Use tables and figures, but focus on the interesting and important results. Make sure you describe in the text what the reviewers should see, explain what the reader sees in the tables and point to the interesting findings. Be explicit about your research question and hypothesis, and discuss they might be true, or false. 
- Led to ? 98\%  name comparison 99\% class comparison 100\%

- Intuitively, our ontology should have had more matches with group 10, since they model the exact same datasets as we do. However, they model the details of events as Entities, while we do it as Properties. To the best of our knowledge, AML cannot match entities to properties. This discovery raises more serious questions since the limitations of matching are evident when design decisions like the ones in this case rigidly prevent matches.

- Matches to ill formed ontologies are hard to predict. For example, Group 15 has two Venues entities which are matched to our single Venue entity in a cyclic way.

\section{Conclusion}
%Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
- 
- Note: the field is messy and outdated tools are often referred.

>>>>

\section{Related Work}
\label{related_work}
%Give here an overview over related matching methods and how they related to your own solution. Cite papers that might have inspired your approach. Sometimes it makes sense to have this section immediately after the introduction.
In order to match our ontology to others, we did research about state of the art matching and alignment tools. \cite{adaptiveInformation_2014} is a comprehensive list of the top 50 tools, separating active from inactive tools. Additionally, we looked at some of the tools revised by Euzenat et Al \cite{euzenat2007ontology}. Furthermore, we looked at the participants from the most recent OAEI.

@@

\section{Methods, Algorithms and Implementation}
% Introduce your method, i.e. the overall approach taken and the general idea, the\bibliography{paper} algorithms in general, maybe in pseudo-code and give a quick overview over the technical implementations (not too much details).
With the results from our Related Work research, we selected AML for ontology matching and SILK for ontology alignment. The similarity measures applied for both of the above were studied from \cite{sun2015comparative}.

% Maybe you want to separate this part into subsections for your two systems
\subsection{Ontology Matching}
\label{Ontology_Matching}
Looking at the most recent OAEI results, we decided to use one of the best candidates in the OAEI of 2014: AML. This tool performed the best for lightweight ontologies, as measured in terms of F-measure. The reasons behind this choice are that AML exceeded our expectations with regard to run time results, comprehensive user interface and integrated evaluation mechanism. The procedure can be fully or semi automatic, with the user being presented to a fully customizable matching. A lexical matching is always performed, followed by other metrics the user can choose from, ranging from structure to content based and others. Furthermore, AML provides with visualizations for the matches as shown in Figure \ref{fig:single_match}, \ref{fig:multiple_match} and \ref{fig:incorrect_match}.
%examples with pictures, String Matcher, Word matcher, Property matcher, Cardinality matcher and background knowledge matcher.

\begin{figure}[h]\centering
	\includegraphics[width=.8\textwidth]{img/match_city.png}
	\caption{Visual representation of a single correct match in AML.}
	\label{fig:single_match}
%\end{figure}
%\begin{figure}[h] \centering
	\includegraphics[width=.8\textwidth]{img/match_combo.png}
	\caption{Visual representation of multiple correct matches in AML.}
	\label{fig:multiple_match}
%\end{figure}
%\begin{figure}[h] \centering
	\includegraphics[width=.8\textwidth]{img/conflict_exhibition_exposition.png}
	\caption{Visual representation of an incorrect match in AML.}
	\label{fig:incorrect_match}
\end{figure}

The power of AML is shown as its ability to combine different types of matchers, in a hierarchical or concurrent manner. Our method was to test each matcher separately in order to study the results obtained, while in a later stage we experimented with different combination of matching (i.e. Word matching, String matching and Structural matching). Furthermore, AML also allows the user to customize the settings of the matchers. For example, regarding String matcher it gives the option to choose between four different similarity measures: iSub, Levenstein, Jaro-Winkler and Q-gram, as described by Sun et al. \cite{sun2015comparative}.

@@

\section{Validation and Experiments}
% In a scientific paper you want to show that your choice of method and algorithms was the right choice. So, this could be a place where you make claims or ask concrete and explicit research questions (e.g. with respect to runtime and/or precision/recall.
We conducted a variety of experiments regarding the matching of our ontology (consisting of 16 classes, 24 properties and 6 individuals) to others. This was made possible by how customizable AML is.

We tried different similarity measures for String and Word matching as well as different filters regarding cardinality and coherence. Results mostly remained unchanged, and we believe this is due to the limited size and complexity of the ontologies presented. However, it is worth mentioning that strict, permissive and hybrid cardinality filters had a significant impact on the resulting alignment. For example, with regards to the matching with group 15, hybrid or permissive filters matched our Event class with 3 different classes of their ontology while with strict filter, we got a single match.

AML also has the ability to evaluate a certain match with respect to a reference match. This gives the option to the end user to manually force or evaluate the match and thus supervise and validate the final match. As so, the user can match classes or properties by hand and use the corrected match as reference for future matchings.

Hereby we report the results for the best matched alignments to the three selected ontologies. Basic characteristics for the ontologies, as well as a visualization of the matching in AML are given for each case.

\subsection{Group 10: Cultural Ontology}
This ontology consists of 11 classes, 23 properties, 1 individual. Our ontology matches to their main entities of Events and Venues.

\begin{figure}[h]\centering
	\includegraphics[width=.7\textwidth]{img/match_g10.png}
	\caption{Matching to group 10}
	\label{fig:match_g10}
\end{figure}

AML found two mappings leading to the following evaluation metrics:

\begin{center}
	\begin{tabular}{| c | c | c |}
		\hline
		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
		100\% & 100\% & 100\% \\ \hline
	\end{tabular}
\end{center}

\subsection{Group 13: Tourist safety Ontology}
This ontology consists of 16 classes, 20 properties, 973 individuals. We matched Events, Location, City as well as Start and End date. The entity for Country was mistakenly matched to the Area entity.

\begin{figure}[h]\centering
	\includegraphics[width=.7\textwidth]{img/match_g13.png}
	\caption{Matching to group 13}
	\label{fig:match_g13}
\end{figure}

AML found 6 mappings, leading to the following evaluation metrics:

\begin{center}
	\begin{tabular}{| c | c | c |}
		\hline
		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
		83.3\% & 100\% & 90.9\% \\ \hline
	\end{tabular}
\end{center}

\subsection{Group 15: Activity finding Ontology}
In this case, the target ontology consists of 66 classes, 599 properties and 57 individuals. This is, by far, a larger ontology than ours and the previous examined ontologies.

\begin{figure}[h]\centering
	\includegraphics[width=.7\textwidth]{img/match_g15.png}
	\caption{Matching to group 15}
	\label{fig:match_g15}
\end{figure}

AML found 12 mappings, six correct versus six incorrect matchings, leading to the following evaluation metrics:

\begin{center}
	\begin{tabular}{| c | c | c |}
		\hline
		\textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\ \hline
		54.5\% & 46.2\% & 50.0\% \\ \hline
	\end{tabular}
\end{center}

\section{Results and Discussion}
% Give here details about the most important results of your experiments. Use tables and figures, but focus on the interesting and important results. Make sure you describe in the text what the reviewers should see, explain what the reader sees in the tables and point to the interesting findings. Be explicit about your research question and hypothesis, and discuss they might be true, or false. 
From the previous section we conclude that the ontology for group 13 matches the best to our ontology since it has the highest number of matches with the least number of mismatches. Yet, the matching only works for one of our three basic entities (Events, Venues and Parking Spots).

Moreover, conflicting with our initial hypothesis, the matching with the group 10's ontology did not perform as well as expected. Intuitively, we believed that our ontology should have had more matches with this group, since they model the same datasets as we do. However, they model characteristics of events as Entities (such as Image, Description and Time Period), while we do it as Properties. To the best of our knowledge, AML cannot match entities to properties. This discovery raises more serious questions since the limitations of matching are evident when design decisions like the ones in this case rigidly prevent proper matching and alignment.

A different problem occurs in the case of the matching to the ontology of group 15. In this case, we found overmatching since their ontology has duplicate classes for Venue and Event. Therefore, several metrics failed to distinguish the duplicate match resulting in AML outputting misleading results. This matching required the most amount of work regarding experimenting and tuning of matching. As stated before, details as fine as the specific type of cardinality filter greatly affected the end result.

\section{Conclusion}
%Here you summarize the preceding sections, describe the lessons learnt and discuss future work.
In this paper we matched our ontology for finding Handicap Parking Spots in Amsterdam to other ontologies related to entertainment in Amsterdam. We found that the match with the highest confidence corresponds to Group 10, but the match with highest overlap corresponds to Group 15 closely followed by Group 13.

From the experiments performed we learned that great amount of work is invested in applying the correct similarity measures.

Furthermore, our experience is backed up by the findings described in Section \ref{related_work}. As we see, Ontology matching is a growing field, that comes up with new promising tools every year. Yet, follow up is not consistent and a robust solution for automatic, or semi-automatic ontology matching has yet to be developed.
